Global Value Chain Analysis of LMICs

### 2016-04-07 Draft.tex

Our analysis confirms the expansion of GVCs in recent years and presents evidence that GVCs have become longer over time. However, we also find that these developments are increasingly driven by low- and middle-income countries while the integration of high-income countries has begun to even out at a high level.

@@

>>>>

Our analysis confirms the expansion of GVCs in recent years and presents evidence that GVCs have become longer over time. We also find that these developments are increasingly driven by low- and middle-income countries while the integration of high-income countries has begun to even out at a high level.

@@

In this section we confirm standard stylized facts of GVC integration that are typically based on smaller samples with OECD ICIO data. We starting by look at the development of two basic measures of GVC integration introduced by \citet{dahuetal01}, namely $fvax$ and $dvar$. Both show the well-known increase
